$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-05-06 paper/paper.tex
Complete example todos

\begin{example}[Variable reference]
  Let us illustrate the use of variable reference relations with an example in \autoref{lst:channels}.
  \begin{lstlisting}[label=lst:channels,mathescape,numbers=left,caption=Variable referece]
  _ : $\contains{\constr{[]} \comma \channel{\unit}{\li} \comma \unit} {\constr{[]} \comma \lio \comma \lio} {\suc \; \constr{0}} {\channel{\unit}{\li}} {\li} {\constr{[]} \comma \lo \comma \lio}$
  _ = $\suc \; \constr{0}$
  \end{lstlisting}
  The underscore \_ introduces an anonymous declaration immediately followed by its definition.
  The constructor $\suc$ steps under the outermost variable in the context, preserving its usage annotation $\lio$ from input to output.
  The constructor $\constr{0}$ asserts that the next variable is of a channel type $\channel{\unit}{\li}$, and that we can split its input annotation $\lio$, taking away $\li$ and leaving $\lo$ as the leftover, to be used later on.
  \todo{use the caption to give a name to the example, not to comment much. Complete/change the incomplete name that I gave}
\end{example}

@@

  \begin{lstlisting}[label=lst:derivation,mathescape,numbers=left,caption= A typing derivation]
  $\func{p}$ : $\Process_1$
  $\func{p}$ = $\new{}$
       $(\comp{\recv{\constr{0}} (\recv{\constr{0}} \PO)}$
       ${\new{} (\send{\suc \; \constr{0}} {\constr{0}} (\send{\constr{0}}{\suc \; \suc \; \constr{0}}) \; \PO)})$

>>>>

\begin{example}[Variable reference]
  Let us illustrate the use of variable reference relations with an example in \autoref{lst:channels}.
  \begin{lstlisting}[label=lst:channels,mathescape,numbers=left,caption=Typing variable reference $\suc \constr{0}$ with type $\channel{\unit}{\li}$ and usage $\li$.]
  _ : $\contains{\constr{[]} \comma \channel{\unit}{\li} \comma \unit} {\constr{[]} \comma \lio \comma \lio} {\suc \; \constr{0}} {\channel{\unit}{\li}} {\li} {\constr{[]} \comma \lo \comma \lio}$
  _ = $\suc \; \constr{0}$
  \end{lstlisting}
  The underscore \_ introduces an anonymous declaration immediately followed by its definition.
  The constructor $\suc$ steps under the outermost variable in the context, preserving its usage annotation $\lio$ from input to output.
  The constructor $\constr{0}$ asserts that the next variable is of a channel type $\channel{\unit}{\li}$, and that we can split its input annotation $\lio$, taking away $\li$ and leaving $\lo$ as the leftover, to be used later on.
  \todo{use the caption to give a name to the example, not to comment much. Complete/change the incomplete name that I gave}
\end{example}

@@

  \begin{lstlisting}[label=lst:derivation,mathescape,numbers=left,caption=Typing a process that sends part of one channel over another.]
  $\func{p}$ : $\Process_1$
  $\func{p}$ = $\new{}$
       $(\comp{\recv{\constr{0}} (\recv{\constr{0}} \PO)}$
       ${\new{} (\send{\suc \; \constr{0}} {\constr{0}} (\send{\constr{0}}{\suc \; \suc \; \constr{0}}) \; \PO)})$
